Applying the optimized ensemble histogram method to the square-well liquid

### 2014-11-05 papers/square-well-liquid/histogram-paper.tex

@@

\textcolor{red}{I think maybe we only want to keep ``pushing down the
  bubbles'' so long as the variance increases.  I'm afraid that if the
  variance drops we could possibly create a dangerous hole when we try
  pushing down a sharp and pointy bubble...}

>>>>

\newcommand{\red}[1]{{\bf \color{red} #1}}
\newcommand{\green}[1]{{\bf \color{green} #1}}
\newcommand{\blue}[1]{{\bf \color{blue} #1}}
\newcommand{\cyan}[1]{{\bf \color{cyan} #1}}

\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\mpsays}[1]{{\color{red} [\blue{Michael:} \emph{#1}]}}

@@

\davidsays{I think maybe we only want to keep ``pushing down the
  bubbles'' so long as the variance increases.  I'm afraid that if the
  variance drops we could possibly create a dangerous hole when we try
  pushing down a sharp and pointy bubble...}

\mpsays{(14 November 2014): I tried running the bubble pushing method
  with the end condition that the added log-space weight gaussian has
  a width 0.5 times that of our energy range (maximum entropy to low
  energy points), and this is precisely what happened: the simulation
  got stuck pushing down sharp and pointy bubbles. Other observations:
  the largest gaussian width ever observed was 0.27 times the energy
  range ($\lambda=1.3$, $\eta=0.3$, $N=20$). Gaussian width also
  jumped around a good deal during initialization, and I might have to
  make some figures to see what exactly happens to it during
  initialization.}
